---
title: "HW2"
author: "KailinXu and LingchenMeng"
date: "2024-09-26"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

[github]()

```{r message=FALSE}
library(tidyverse)
library(gtrendsR)
library(censusapi)
library(httr)
library(ggplot2)
```

Pulling from APIs\large
```{r}
res <- gtrends(c("crime", "loans"), 
               geo = "US-IL", 
               time = "2020-01-01 2020-12-31", 
               low_search_volume = TRUE)
plot(res)
```


Answer the following questions for the keywords "crime" and "loans".  
Find the mean, median and variance of the search hits for the keywords.
```{r}
res_time <- res$interest_over_time
res_time %>% group_by(keyword) %>% summarise(mean=mean(hits),median=median(hits),
                                             variance=var(hits))
```

Which cities (locations) have the highest search frequency for loans?  
Evergreen Park
```{r}
res_city <- res$interest_by_city
res_city %>% filter(keyword=='loans', !is.na(hits)) %>% arrange(hits) %>% tail(5)
```


Is there a relationship between the search intensities between the two keywords we used?   

There is no significant linear relationship between the search intensity of these two keywords,since the correlation coefficient is -0.1947519, which is a negative correlation close to 0. although there is some negative correlation trend, but the correlation is weak.
```{r}
res_2 <- spread(res$interest_over_time, key = 'keyword', value = 'hits', fill=0)
cor(res_2$crime, res_2$loans)
plot(res_2$crime, res_2$loans,
     main = "Relationship Between Search Popularity of 'Crime' and 'Loans'",
     xlab = "Search Hits for 'Crime'",
     ylab = "Search Hits for 'Loans'")
```

Repeat the above for keywords related to covid. Make sure you use multiple keywords like we did above. Try several different combinations and think carefully about words that might make sense within this context.
```{r}
mask <- gtrends(c("covid","mask"), 
               geo = "US-IL", 
               time = "2020-01-01 2020-12-31", 
               low_search_volume = TRUE)
plot(mask)
```
The mean, median and variance of the search hits for 'cobid' and 'mask' are as below.
```{r}
mask_time <- mask$interest_over_time
mask_time$hits <- as.numeric(mask_time$hits)
mask_time %>% group_by(keyword) %>% 
  summarise(mean=mean(hits,na.rm = TRUE),
            median=median(hits,na.rm = TRUE),
            variance=var(hits,na.rm = TRUE))
```
Pesotum has the highest search frequency for covid.
```{r}
mask_city <- mask$interest_by_city
mask_city %>% filter(keyword=='covid', !is.na(hits)) %>% arrange(hits) %>% tail(5)
```
The correlation between "covid" and "mask" is 0.56059,indicating a moderate positive correlation.
```{r}
mask_2 <- spread(mask_time, key = 'keyword',value = 'hits', fill=0)
cor(mask_2$covid, mask_2$mask)
plot(mask_2$covid, mask_2$mask,
     main = "Relationship Between Search Popularity of 'Covid' and 'Mask'",
     xlab = "Search Hits for 'Covid'",
     ylab = "Search Hits for 'Mask'")
```


Google Trends + ACS\large
```{r}
cs_key <- read_file("census-key.txt")
```

```{r}
acs_il <- getCensus(name = "acs/acs5",
                    vintage = 2020, 
                    vars = c("NAME", 
                             "B01001_001E", 
                             "B06002_001E", 
                             "B19013_001E", 
                             "B19301_001E"), 
                    region = "place:*", 
                    regionin = "state:17",
                    key = cs_key)
head(acs_il)
```

```{r}
acs_il[acs_il == -666666666] <- NA
```

```{r}
acs_il <-
  acs_il %>%
  rename(pop = B01001_001E, 
         age = B06002_001E, 
         hh_income = B19013_001E, 
         income = B19301_001E)
```

We first have to clean NAME so that it has the same structure as location in the search interest by city data. Add a new variable location to the ACS data that only includes city names.
```{r}
acs_il2 <- separate(acs_il, col = NAME, into = c('location','state'), sep = ',')
acs_il2$location <- word(acs_il2$location, start = 1, end = -2)
head(acs_il2)
```

First, check how many cities don't appear in both data sets, i.e. cannot be matched. Then, create a new data set by joining the Google Trends and the ACS data. Keep only cities that appear in both data sets.  

1138.
```{r}
res_city_w <- spread(res$interest_by_city, key = 'keyword', value = 'hits')
unmatch1 <- anti_join(acs_il2, res_city_w, by= 'location')
unmatch12 <- anti_join(res_city_w,acs_il2,by= 'location')
total_unmatched <- nrow(unmatch1) + nrow(unmatch12)
total_unmatched
match_1 <- inner_join(acs_il2, res_city_w, by = 'location')
head(match_1)
```

Compute the mean of the search popularity for both keywords for cities that have an above average median household income and for those that have an below average median household income. When building your pipe, start with creating the grouping variable and then proceed with the remaining tasks. What conclusions might you draw from this?  
  
  The search popularity of "crime" and "loans" is slightly higher in high-income cities than in low-income cities. There may be a relationship between income level and search popularity, but the difference is not particularly large.
```{r}
avg_hh <- mean(match_1$hh_income, na.rm = TRUE)
match_1$group <- ifelse(match_1$hh_income>avg_hh,'above','below')
match_1 %>% group_by(group) %>% summarise(mean_crim = mean(crime,na.rm = TRUE), 
                                          mean_loan = mean(loans,na.rm = TRUE))
```
Is there a relationship between the median household income and the search popularity of the Google trends terms? Describe the relationship and use a scatterplot with qplot().  
As the median household income increases, there is an upward trend in the search popularity. This suggests that cities with higher household incomes may have higher search activity, especially in the high income range.
```{r}
res_city_clean <- res_city %>% group_by(location) %>% summarise(total=sum(hits))
match_2 <- inner_join(acs_il2, res_city_clean, by = 'location')
qplot(hh_income, total, data=na.omit(match_2),
      geom = c("point", "smooth"),
      main = 'relationship between the median household income and the search popularity',
      xlab = 'income', ylab='hits')
```

Repeat the above steps using the covid data and the ACS data.
1154 cities don't appear in both data sets.
```{r}
covid_2 <- spread(mask$interest_by_city, key = 'keyword', value = 'hits')
unmatch3 <- anti_join(acs_il2, covid_2, by= 'location')
unmatch4 <- anti_join(covid_2,acs_il2,by= 'location')
total_unmatch_covid <- nrow(unmatch3) + nrow(unmatch4)
total_unmatch_covid
match_covid <- inner_join(acs_il2, covid_2, by = 'location')
head(match_covid)
```

The search popularity of "covid" is slightly higher in high-income cities than in low-income cities. But the situation for "mask" is the opposite.
```{r}
avg_hh2 <- mean(match_covid$hh_income, na.rm = TRUE)
match_covid$group <- ifelse(match_covid$hh_income > avg_hh,'above','below')
match_covid %>% group_by(group) %>% summarise(mean_covid = mean(covid,na.rm = TRUE), 
                                          mean_mask = mean(mask,na.rm = TRUE))
```

There is a positive correlation between median household income and search popularity.
```{r}
mask_city_clean <- mask_city %>% group_by(location) %>% summarise(total=sum(hits))
match_covid2 <- inner_join(acs_il2, mask_city_clean, by = 'location')
qplot(hh_income, total, data=na.omit(match_covid2),
      geom = c("point", "smooth"),
      main = 'relationship between the median household income and the search popularity',
      xlab = 'income', ylab='hits')
```

